---
title: "Final Project"
author: "Anmay Gupta"
date: "6/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(primer.data)
library(lubridate)
library(janitor)
library(skimr)
library(rvest)
library(gapminder)
library(forcats)
source("functions.R")
```

Okay, so right now my plan is to go through certain 3D printer recommendations  
I would do this by looking at the 10 printers listed [here](https://www.3dsourced.com/rankings/best-fdm-3d-printer/)
I'm safe if I cite them because their robots.txt file only disallows visiting admin pages
Which means that their data is free for the pickings

Here's an example of what their data looks like:
I'm using these CSS selectors: #tablepress-10 .column-1:

```{r}
page <- read_html("https://www.3dsourced.com/rankings/best-fdm-3d-printer/")
printer_names <- html_nodes(page, "#tablepress-10 .column-1")
printer_text <- html_text(printer_names)
printers <- printer_text[2:11]
printers
```

New plan:  
There's not nearly enough data to compare these printers by, so I'm gonna do something else
I'm going to find every single printer that All3DP, one of the main 3d printer review companies, has reviewed
All3DP has a clear robots.txt file that lets me access everything so it should be fine
Then I can look at those reviews, take out all of the printer names, and go by that
Website: https://all3dp.com/reviews/page/1
CSS selector: .headline--l

<!-- From https://www.datacamp.com/community/tutorials/r-web-scraping-rvest -->
```{r}
list_of_pages <- str_c("https://all3dp.com/reviews/page/", 1:20)
review_names <- list_of_pages %>%
                    map(read_page_names, ".headline--l")
names(review_names) <- letters[1:20]
review_names
```














