---
title: "Final Project"
author: "Anmay Gupta"
date: "6/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(primer.data)
library(lubridate)
library(janitor)
library(skimr)
library(rvest)
library(gapminder)
library(forcats)
source("functions.R")
```

Okay, so right now my plan is to go through certain 3D printer recommendations  
I would do this by looking at the 10 printers listed [here](https://www.3dsourced.com/rankings/best-fdm-3d-printer/)
I'm safe if I cite them because their robots.txt file only disallows visiting admin pages
Which means that their data is free for the pickings

Here's an example of what their data looks like:
I'm using these CSS selectors: #tablepress-10 .column-1:

```{r}
page <- read_html("https://www.3dsourced.com/rankings/best-fdm-3d-printer/")
printer_names <- html_nodes(page, "#tablepress-10 .column-1")
printer_text <- html_text(printer_names)
printers <- printer_text[2:11]
printers
```

New plan:  
There's not nearly enough data to compare these printers by, so I'm gonna do something else
I'm going to find every single printer that All3DP, one of the main 3d printer review companies, has reviewed
All3DP has a clear robots.txt file that lets me access everything so it should be fine
Then I can look at those reviews, take out all of the printer names, and go by that
Website: https://all3dp.com/reviews/page/1
CSS selector: .headline--l

<!-- From https://www.datacamp.com/community/tutorials/r-web-scraping-rvest -->
<!-- Keep in mind that if All3DP asks you to name your user agent to do rvest::user_agent()-->
```{r}
list_of_pages <- str_c("https://all3dp.com/reviews/page/", 1:20)
review_names <- list_of_pages %>%
                    map(read_page_names, ".headline--l")
names(review_names) <- letters[1:20]
review_names
```
Now that I have the review names, I need to choose the ones that actually have to do with a 3D printer
Basically, I'm just going to filter so that the title contains review and doesn't include bad things
For example, "filament", "scanner", "CNC", etc
After that, I can get a subreddit using the brand name
The brand name will just be the company name
So Phrozen, Creality, etc

Then I go through it, look for the number of issues with the printer and graph it

## **New New Plan**

Go onto amazon, search "3D printer" and go by that
You can graph the listings, the ratings, even look at the feature list
This makes a lot more sense and is a lot easier than the other options
And Amazon has a full on API that it can use!

Just use the "paws" package and create an account with Amazon Warehouse Services
For extra credit, do the subreddit thing as well! That works too!
This way you can create a lot of really interesting graphs and get the best 3D printer!

## **The subreddit thing is genuinely smart because it has a cool idea**
This way you can look at something without bots and with genuine issues
The problem is going to be getting the printer name itself from the package
Something like Official Creality Ender 3 V2 Upgraded 3D printer Integrated... vs Ender 3 V2 is what we want
But it's going to be pretty hard to get, especially considering there could be multiple listings for the same product

## **This way we can do cool things**





















